QALY Comparison - Living Wage Intervention

### 2023-11-02 minos/testing/QALY_comparison_livingWage.Rmd
Seeded mortality to negate the potential effect in QALY calculations

ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = total_boost, group = intervention, colour = intervention)) +
  geom_smooth()
```

@@

```{r}
combined.cost <- combined %>%
  select(-pop_size, -SF_12_MCS, -SF_12_PCS, -utility) %>%
  mutate(QALY_value = QALYs * 60000)

@@

combined.cost.change <- combined.cost %>%
  select(-total_boost, -QALYs) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'QALY_value') %>%
  mutate(change_baseline = baseline - baseline,
         change_LivingWage = livingWageIntervention - baseline) %>%
  select(-baseline, -livingWageIntervention) %>%
  pivot_longer(cols = change_baseline:change_LivingWage,
               names_to = 'intervention',
               names_prefix = 'change_',
               values_to = 'QALY_value_change') %>%
  filter(intervention != 'baseline')

@@

ICER <- combined.cost.mean %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
  mutate(ICER = (total_boost_livingWageIntervention - total_boost_baseline) / (QALYs_livingWageIntervention - QALYs_baseline)) %>%
  select(run_id, year, ICER) %>%
  mutate(intervention = 'LivingWage')

>>>>

ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = total_boost, group = intervention, colour = intervention)) +
  geom_smooth()

ggplot(combined, aes(x = year, y = alive_ratio, group = intervention, colour = intervention)) +
  geom_smooth()
```

@@

```{r}
combined.cost <- combined %>%
  select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
  mutate(QALY_value = QALYs * 60000)

@@

combined.cost.change <- combined.cost %>%
  select(run_id, year, intervention, QALY_value) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'QALY_value') %>%
  mutate(change_baseline = baseline - baseline,
         change_LivingWage = livingWageIntervention - baseline) %>%
  select(-baseline, -livingWageIntervention) %>%
  pivot_longer(cols = change_baseline:change_LivingWage,
               names_to = 'intervention',
               names_prefix = 'change_',
               values_to = 'QALY_value_change') %>%
  filter(intervention != 'baseline')

@@

ICER <- combined.cost.mean %>%
  select(run_id, year, intervention, total_boost, QALYs, QALY_value) %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
  mutate(ICER = (total_boost_livingWageIntervention - total_boost_baseline) / (QALYs_livingWageIntervention - QALYs_baseline)) %>%
  select(run_id, year, ICER) %>%
  mutate(intervention = 'LivingWage')
